Probability

### 2016-04-10 prob.tex
prob.tex "Example 6. [Quantum probability measure]" update...

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the probability
of each electron is not independent, i.e., we cannot find three probability
space for each subsystem such that 
\[
\mathbb{P}_{xxx}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
\]
Correlated variables are also common in the classical world. For example,
if the first coin is head or tail decided by whether the temperature
is higher than a particular degree and the second coin is decided
by whether Coca Cola is sold more than a particular amount, then we
know these two coins are correlated. Einstein, Podolsky, and Rosen
(EPR)~\cite{EPR1935} suggested any correlated quantum probability
results may be interpreted classically. For example, the nature might
roll an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its four faces.
If $LRR$ were face-down, the measurement result for three electrons
would be $L$, $R$, and $R$, respectively. Furthermore, this tetrahedron
die might not be accessed by human for some reasons so that we think
we are handling a system constituting three electrons.

>>>>

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the probability
measure of the space cannot be expressed as the product of the probability
measure of each electron, i.e., 
\[
\mathbb{P}_{xxx}(\{abc\})\ne\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
\]
Correlated variables are also common in the classical world. For example,
if the first coin is head or tail decided by whether the temperature
is higher than a particular degree and the second coin is decided
by whether Coca Cola is sold more than a particular amount, then we
know these two coins are correlated. Einstein, Podolsky, and Rosen
(EPR)~\cite{EPR1935} suggested any correlated quantum probability
results may be interpreted classically. For example, the nature might
roll an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its four faces.
If $LRR$ were face-down, the measurement result for three electrons
would be $L$, $R$, and $R$, respectively. Furthermore, this tetrahedron
die might not be accessed by human for some reasons so that we think
we are handling a system constituting three electrons.
